---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# fpp3

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fpp3)](https://cran.r-project.org/package=fpp3)
[![Travis build status](https://travis-ci.org/robjhyndman/fpp3-package.svg?branch=master)](https://travis-ci.org/robjhyndman/fpp3-package)
<!-- badges: end -->

## Overview

The fpp3 package contains data used in the book [*Forecasting: Principles and Practice* (3rd edition)](https://OTexts.com/fpp3) by Rob J Hyndman and George Athanasopoulos. It also loads several packages needed to do the analysis described in the book. These packages work with the [tidyverse](https://www.tidyverse.org/) set of packages, sharing common data representations and API design.

## Installation

```{r eval = FALSE}
# Currently, only the development version is available on GitHub.
# Some of the component packages are also only available on GitHub.
# install.packages("remotes")
remotes::install_github("robjhyndman/fpp3-package")
```

## Usage

`library(fpp3)` will load the following packages:

* [tibble](http://tibble.tidyverse.org), for tibbles, a modern re-imagining of data frames.
* [dplyr](http://dplyr.tidyverse.org), for data manipulation.
* [tidyr](http://tidyr.tidyverse.org), to easily tidy data using `spread()` and `gather()`.
* [lubridate](https://github.com/hadley/lubridate), for date/times.
* [ggplot2](http://ggplot2.tidyverse.org), for data visualisation.
* [tsibble](http://tsibble.tidyverts.org), for tsibbles, a time series version of a tibble.
* [tsibbledata](http://tsibbledata.tidyverts.org), various time series data sets in the form of tsibbles.
* [feasts](http://feasts.tidyverts.org), for features and statistics of time series.
* [fable](http://fable.tidyverts.org), for fitting models and producing forecasts.

You also get a condensed summary of conflicts with other packages you have loaded:

```{r example}
library(fpp3)
```

